Combined Task and Motion Planner through an Interface Layer

### 2015-05-12 documentation/ps4.tex
limitations

>>>>

The interface does not scale well to large object state spaces, as this increases the number of geometric constraints. 
This increase in geometric constraints causes the number of motion planner calls to explode, slowing down the planning stage. 
In addition, in its current implementation it only works within deterministic, fully-observable environments and is infeasible for online replanning.
